---
title: "vmodern Theme"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  vthemes::vmodern:
    code_folding: show
    lightbox: true
# pkgdown:
#   as_is: true
# vignette: >
#   %\VignetteIndexEntry{vmodern}
#   %\VignetteEngine{knitr::rmarkdown}
#   %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
library(knitr)
library(vthemes)
library(ggplot2)
library(dplyr)

## Global options
options(max.print = "80")
knitr::opts_chunk$set(
  echo = TRUE, 
  cache = FALSE, 
  message = FALSE, 
  warning = FALSE
)
opts_knit$set(width = 80)
```

# Code Styling

### Syntax Highlighting

Code with syntax highlighting:

```{r sh}
hello <- function(name) {
  cat(sprintf("Hello, %s!", name))
}

hello("world")
```

### Verbatim Output

```{r iris-str}
str(iris)
```

# Markdown

A list:

1. One
2. Two
3. Three
    - hello
    - world

**bold**, *italics*, <del>strikethrough</del>.

A blockquote :

> Hello! This is a blockquote.

A [link](https://www.r-project.org/) or url: https://www.r-project.org/

Some math:

\begin{align*}
y = X\beta + \epsilon
\end{align*}

Now some headers:

## Level 2

### Level 3

#### Level 4

##### Level 5


# Tabsets

The `vmodern` R markdown theme comes with five preset tab styles.

- Traditional Tabs: `{.tabset}`
- Traditional Pills: `{.tabset .tabset-pills}`
- Modern Tabs: `{.tabset .tabset-vmodern}`
- Modern Square Pills: `{.tabset .tabset-pills .tabset-square}`
- Modern Circle Pills: `{.tabset .tabset-pills .tabset-circle}`

## Traditional {.tabset}

### Tab 1

### Tab 2

### Tab 3

## Pills {.tabset .tabset-pills}

### Tab 1

### Tab 2

### Tab 3

## vmodern Tabs {.tabset .tabset-vmodern}

### Tab 1

### Tab 2

### Tab 3

## Grey Square Tabs {.tabset .tabset-pills .tabset-square}

### Tab 1

### Tab 2

### Tab 3

## Grey Circle Tabs {.tabset .tabset-pills .tabset-circle}

### Tab 1

### Tab 2

### Tab 3


# Figures

A plot using the `vmodern` ggplot2 theme and a caption:

```{r iris-fig, fig.cap = "A caption", fig.width = 8, fig.height = 4}
ggplot(iris) +
  aes(x = Sepal.Length, y = Sepal.Width, color = Species) +
  geom_point() +
  theme_vmodern() +
  scale_color_vmodern(discrete = TRUE)
```

A sequence of plots generated in a for loop using `subchunkify()`:

```{r iris-subchunkify, results = "asis"}
for (feature in setdiff(colnames(iris), "Species")) {
  hist_plot <- ggplot(iris) +
    aes(x = .data[[feature]]) +
    geom_histogram(bins = 12, color = "grey98", fill = "#3B7EA1") +
    labs(y = "Frequency", title = feature) +
    theme_vmodern()
  subchunkify(hist_plot, i = sprintf("histogram-%s", feature), 
              fig_height = 4, fig_width = 8)
}
```


# Tables

A table using `pretty_kable()`:

```{r table-kable}
iris %>%
  group_by(Species) %>%
  summarise(across(.fns = mean)) %>%
  pretty_kable(
    digits = 2, 
    sigfig = FALSE,
    caption = "Mean of each iris feature with the maximum value bolded in blue", 
    format = "html", 
    bold_margin = 2, 
    bold_function = ". == max(.)",
    bold_color = "red",
    bold_scheme = c(FALSE, TRUE, TRUE, TRUE, TRUE)
  )
```

A table using `pretty_DT()`:

```{r table-dt}
pretty_DT(iris, digits = 2, sigfig = FALSE, 
          caption = "Iris dataset", rownames = FALSE)
```

Note that both `pretty_kable()` and `pretty_DT()` enable convenient bolding options.



